Favourable Conservation Status (FCS): <br> Analysis of Bauer et al. (unpublished) Field experiment

### 2022-12-02 R/model_fcs_check.Rmd
Update

---
title: "Favourable Conservation Status (FCS): <br> Analysis of Bauer et al. (unpublished) Field experiment"
author: "Markus Bauer <br>"
date: "`r format(Sys.time(), '%Y-%m-%d')`"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

FCS sensu Helm et al. (2015) https://doi.org/10.1111/ddi.12285

@@

```{r message = FALSE, tidy = TRUE}
library(here)
library(tidyverse)
library(ggbeeswarm)
library(patchwork)
library(brms)
library(DHARMa)
library(DHARMa.helpers)
library(bayesplot)
library(loo)
library(tidybayes)
library(emmeans)
```

@@

```{r}
load(file = here("outputs", "models", "model_fcs_2.Rdata"))
load(file = here("outputs", "models", "model_fcs_full.Rdata"))
```

### Model comparison

```{r}
m_1 <- m2
m_2 <- m_full
```

Model forumlas for m_1 and m_2

```{r tidy = FALSE}
m_1$formula
m_2$formula
```

Possible prior distributions

```{r}
ggplot(data = data.frame(x = c(-1, 1)), aes(x = x)) +
  stat_function(fun = dnorm, n = 101, args = list(mean = 0.1, sd = 1)) +
  expand_limits(y = 0) + ggtitle("Normal distribution")
ggplot(data = data.frame(x = c(-1, 1)), aes(x = x)) +
  stat_function(fun = dcauchy, n = 101, args = list(location = 0, scale = 1)) +
  expand_limits(y = 0) + ggtitle("Cauchy distribution")
ggplot(data.frame(x = c(-1, 1)), aes(x = x)) +
  stat_function(fun = dstudent_t, args = list(df = 3, mu = 0, sigma = 2.5)) +
  expand_limits(y = 0) + ggtitle(expression(Student~italic(t)*"-distribution"))
```

Prior summary

@@

```{r}
bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
         re_formula =  ~ (1 | site/plot) + (1 | botanist_year)) 
bayes_R2(m_2, probs = c(0.05, 0.5, 0.95),
         re_formula =  ~ (1 | site/plot) + (1 | botanist_year))
```

@@

```{r}
bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
         re_formula = 1 ~ 1)
bayes_R2(m_2, probs = c(0.05, 0.5, 0.95),
         re_formula = 1 ~ 1)
```

@@

```{r}
DHARMa.helpers::dh_check_brms(m_1, integer = TRUE)
DHARMa.helpers::dh_check_brms(m_2, integer = TRUE)
```

@@

#### Sampling efficency/effectiveness (Rhat and EFF)

```{r}
range(draws1$rhat)
range(draws2$rhat)
range(draws1$ess_bulk)
range(draws2$ess_bulk)
range(draws1$ess_tail)
range(draws2$ess_tail)
```

@@

```{r}
bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
         re_formula =  ~ (1 | site/plot) + (1 | botanist_year)) 
bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
         re_formula = 1 ~ 1)
```

@@

The system for these calculations

```{r}
sessionInfo()
```

```{r echo = FALSE}
write.csv(draws1, here("outputs", "statistics", "table_fcs_test.csv"))
```

>>>>

---
title: "Favourable Conservation Status (FCS): <br> Analysis of Bauer et al. (unpublished) Field experiment"
author: "Markus Bauer^* <br>"
date: "`r format(Sys.time(), '%Y-%m-%d')`"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  fig.width = 12,
  fig.height = 12,
  dpi = 600
  )
```

Technichal University of Munich, TUM School of Life Sciences, Chair of Restoration Ecology, Emil-Ramann-Straße 6, 85354 Freising, Germany

* Corresponding author: [markus1.bauer@tum.de](mailto:markus1.bauer@tum.de)
<br>
[ORCiD ID: 0000-0001-5372-4174](https://orcid.org/0000-0001-5372-4174)
<br>
[Google Scholar](https://scholar.google.de/citations?user=oHhmOkkAAAAJ&hl=de&oi=ao)
<br>
[GitHub: markus1bauer](https://github.com/markus1bauer)

Favourable Conservation Status (FSC) sensu Helm et al. (2015) Divers Distrib [DOI: 10.1111/ddi.12285](https://doi.org/10.1111/ddi.12285)

@@

```{r message = FALSE}
library(here)
library(tidyverse)
library(ggbeeswarm)
library(patchwork)
library(brms)
library(DHARMa)
library(DHARMa.helpers)
library(bayesplot)
library(loo)
library(tidybayes)
library(emmeans)
```

@@

```{r collapse = TRUE}
load(file = here("outputs", "models", "model_fcs_2.Rdata"))
load(file = here("outputs", "models", "model_fcs_full.Rdata"))
m_1 <- m2
m_2 <- m_full
m_1$formula
m_2$formula
```

### Priors

#### Possible prior distributions

```{r}
ggplot(data = data.frame(x = c(-1, 1)), aes(x = x)) +
  stat_function(
    fun = dnorm, n = 101, args = list(mean = 0.1, sd = 1)
    ) +
  expand_limits(y = 0) + ggtitle("Normal distribution")
ggplot(data = data.frame(x = c(-1, 1)), aes(x = x)) +
  stat_function(
    fun = dcauchy, n = 101, args = list(location = 0, scale = 1)
    ) +
  expand_limits(y = 0) + ggtitle("Cauchy distribution")
ggplot(data.frame(x = c(-1, 1)), aes(x = x)) +
  stat_function(
    fun = dstudent_t, args = list(df = 3, mu = 0, sigma = 2.5)
    ) +
  expand_limits(y = 0) + ggtitle(expression(Student~italic(t)*"-distribution"))
```

#### Prior summary

@@

```{r collapse = TRUE}
bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
         re_formula =  ~ (1 | site/plot) + (1 | botanist_year)) 
bayes_R2(m_2, probs = c(0.05, 0.5, 0.95),
         re_formula =  ~ (1 | site/plot) + (1 | botanist_year))
```

@@

```{r collapse = TRUE}
bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
         re_formula = 1 ~ 1)
bayes_R2(m_2, probs = c(0.05, 0.5, 0.95),
         re_formula = 1 ~ 1)
```

@@

```{r collapse = TRUE}
DHARMa.helpers::dh_check_brms(m_1, integer = TRUE)
DHARMa.helpers::dh_check_brms(m_2, integer = TRUE)
```

@@

#### Sampling efficency and effectiveness

Rhat

```{r collapse = TRUE}
range(draws1$rhat)
range(draws2$rhat)
```

Effective sampling size (ESS)

```{r collapse = TRUE}
range(draws1$ess_bulk)
range(draws2$ess_bulk)
range(draws1$ess_tail)
range(draws2$ess_tail)
```

@@

```{r collapse = TRUE}
bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
         re_formula =  ~ (1 | site/plot) + (1 | botanist_year)) 
bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
         re_formula = 1 ~ 1)
```

@@

```{r echo = FALSE}
write.csv(draws1, here("outputs", "statistics", "table_fcs.csv"))
```

## Session info

```{r echo = FALSE}
sessionInfo()
```
